A generalized definition of multidimensional item response theory parameters

### 2023-02-21 output/paper_draft/paper_M2PLM_parameters.Rmd
Moves the definition of the cosine vectors in the standard basis where they are needed for the first time.

Let's consider now the vectors $`r DIR_COS_VEC`$ and $`r DIR_COS_VEC_STD`$, made
up by the $`r N_DIMS`$ direction cosines of $`r TRAIT_VECTOR`$ with the basis
vectors of $`r LS_BASIS`$ and $`r LS_STD_BASIS`$, respectively.

@@

Let $`r DIR_COS_VEC_ALT`$ be the vector of direction cosines of
$`r TRAIT_VECTOR`$ in $`r ALT_BASIS`$ (i.e., the cosines with the elements of
$`r ALT_BASIS`$).

>>>>

Let's consider now the vector $`r DIR_COS_VEC`$, made up by the $`r N_DIMS`$
direction cosines of $`r TRAIT_VECTOR`$ with
the basis vectors of $`r LS_BASIS`$.

@@

Let $`r DIR_COS_VEC_STD`$ and $`r DIR_COS_VEC_ALT`$ be the vectors of
direction cosines of $`r TRAIT_VECTOR`$ in $`r LS_STD_BASIS`$ and
$`r ALT_BASIS`$, respectively.
